Identifying financial actors: marine case

### 2023-12-14 marine_tipping.Rmd
update with new data

```{r}
load("data/cleaned_data_230708.Rda")
load("data/boats_owners.Rda")
load("data/marine_shareholders.RData")
## some initial visualizations
countries <- readr::read_csv(
    file = "~/Documents/Projects/DATA/WorldBank/SDG_csv/SDGCountry.csv") |> 
    janitor::clean_names()
## correct Namibia
countries[countries$short_name == "Namibia","x2_alpha_code"] <- "NA"

@@

```{r poster, fig.width=8, fig.height=8}
net <- shrs |> 
    filter(!is.na(name), !is.na(country)) |> 
    select(country, name, company) |> 
    left_join(
        df_boats |> 
            select(flag, reg_owner) |> 
            filter(!is.na(reg_owner)) |> 
            unique(),
        by = c("company" = "reg_owner")
    ) |> 
    mutate(flag = str_remove_all(flag, " \\(Int. Register\\)")) |> 
    group_by(country, flag) |> 
    summarize(n = n()) |># print(n=151)
    left_join(countries |> 
                  select(short_name, x2_alpha_code), 
              by = c("country"= "x2_alpha_code")) |> #print(n = 151)
    mutate(short_name = case_when(
        country == "TW" ~ "Taiwan, China",
        TRUE ~ short_name)) |> 
    mutate(flag = case_when(
        flag == "U.K." ~ "United Kingdom",
        flag == "Republic of Ireland" ~ "Ireland",
        flag == "U.S.A." ~ "United States",
        TRUE ~ flag),
        short_name = case_when(
            short_name == "Dem. People's Rep. Korea" ~ "South Korea",
            TRUE ~ short_name
        )) |> 
    ungroup() |> 
    select(from = short_name, to = flag, n) |>
    filter(!is.na(from)) |> #print(n = 151)
    network(directed = TRUE, bipartite = FALSE, matrix.type = "edgelist", 
            ignore.eval=FALSE, loops = TRUE)

>>>>

```{r}
load("data/cleaned_data_231023.Rda")
load("data/boats_owners.Rda")
load("data/marine_shareholders.RData")
## some initial visualizations
countries <- readr::read_csv(
    file = "~/Documents/Projects/DATA/WorldBank/SDG_csv/SDGCountry.csv") |> 
    janitor::clean_names()
## correct Namibia
countries[countries$short_name == "Namibia","x2_alpha_code"] <- "NA"

@@

```{r poster, fig.width=8, fig.height=8}
net <- shrs |> 
    filter(!is.na(name), !is.na(country)) |> 
    select(country, name, company) |> 
    left_join(
        df_boats |> 
            select(flag, reg_owner) |> 
            filter(!is.na(reg_owner)) |> 
            unique(),
        by = c("company" = "reg_owner")
    ) |> filter(!is.na(flag)) |> 
    mutate(flag = str_remove_all(flag, " \\(Int. Register\\)")) |> 
    group_by(country, flag) |> 
    summarize(n = n()) |># print(n=151)
    left_join(countries |> 
                  select(short_name, x2_alpha_code), 
              by = c("country"= "x2_alpha_code")) |> #print(n = 151)
    mutate(short_name = case_when(
        country == "TW" ~ "Taiwan, China",
        TRUE ~ short_name)) |> 
    mutate(flag = case_when(
        flag == "U.K." ~ "United Kingdom",
        flag == "Republic of Ireland" ~ "Ireland",
        flag == "U.S.A." ~ "United States",
        TRUE ~ flag),
        short_name = case_when(
            short_name == "Dem. People's Rep. Korea" ~ "South Korea",
            TRUE ~ short_name
        )) |> 
    ungroup() |> 
    select(from = short_name, to = flag, n) |>
    filter(!is.na(from)) |> #print(n = 151)
    network(directed = TRUE, bipartite = FALSE, matrix.type = "edgelist", 
            ignore.eval=FALSE, loops = TRUE)
